Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings

### 2015-12-08 manuscript/manuscript_pve.Rmd
switched to thesis docx for margins

---
title: "Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: tree-physiology.csl
bibliography: references.bib
---

>>>>

---
title: "Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: tree-physiology.csl
bibliography: references.bib
---
